### 2021-03-18 manuscript/supplementary.tex
Updated manuscript title.

\PaperTitle{Supplementary results for: A meta-analysis of bioinformatics software benchmarks reveals major influences on software accuracy} % Article title

>>>>

\PaperTitle{Supplementary results for: Sustained software development, not number of citations or journal choice, is indicative of accurate bioinformatic software} % Article title
